---
title: "OceanCleaner_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OceanCleaner_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

My package aims to clean and present data in a manageable way. First, the Marine.Clean function cleans the data of any duplicates and NA rows. Then the Pare.down function allows the user to pare down their data to a specific site and month in their data. Finally, the Species.Summary function gives a bar plot with the abundance of the species as well as a summary of the data. 

```{r setup}
library(Ocean.Cleaner)
```
```{r}
head(ReefFish)


```
Using the ReefFish data set and assuming that you would want RedFish in Site1 during January you would do the following:
```{r}
Marine.distinct<- Marine.clean(ReefFish, remove_na= TRUE)

site_data<- Pare.down( Marine.distinct, "January", "Reef1")

Species.Summary(site_data,"Species", "RedFish", "Abundance")

```

